---
title: "Beautifying the Visualization"
author: "Bing-Je_Wu"
date: "8/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```


## Outlines  
  * Modifying the Background  
  * Modifying Axes  
  * Modifying Scales  
  * Modifying Legends  
  * Annotating Plots  
  * Titles  
  * Themes  


##  Modifying the Background  
#### Load the dataset  
```{r}
library(tidyverse)
college <- read_csv('http://672258.youcanlearnit.net/college.csv')
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree),
         control=as.factor(control), gender=as.factor(gender),
         loan_default_rate=as.numeric(loan_default_rate))
```

#### Create the bar graph  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control))
```

#### Change the "plot" background color  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(plot.background=element_rect(fill='green'))
```

#### Change the "panel" background color  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_rect(fill='green'))
```

#### Minimize both backgrounds  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank())
```

#### Add grey gridlines to "panel"  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  theme(panel.grid.major=element_line(color="grey"))
```

#### Show the y-axis gridlines only  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  theme(panel.grid.major.y=element_line(color="grey"))
```






## Modifying Axes  
#### Load the dataset  
```{r}
library(tidyverse)
college <- read_csv('http://672258.youcanlearnit.net/college.csv')
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree),
         control=as.factor(control), gender=as.factor(gender),
         loan_default_rate=as.numeric(loan_default_rate))
```

#### Create the bar graph  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank())
```

#### Rename the axes  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  xlab("Region") +
  ylab("Number of Schools")
```

#### Resize the y-axis  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  xlab("Region") +
  ylab("Number of Schools") +
  ylim(0,500)
```






## Modifying Scales  
*scale_(axis)_(continuous/discrete)*  

*scale_fill_manual*  

*scale_(color/size)_(continuous/discrete)*  

#### Load the dataset  
```{r}
college <- read_csv('http://672258.youcanlearnit.net/college.csv')
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree),
         control=as.factor(control), gender=as.factor(gender),
         loan_default_rate=as.numeric(loan_default_rate))
```

#### Create the bar graph  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank())
```

#### Use scale_ to change the name of x-axis  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  scale_x_discrete(name="Region")
```

#### Use scale_ to change the name and limits of the y-axis  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  scale_x_discrete(name="Region") +
  scale_y_continuous(name="Number of Schools", limits=c(0,500))
```

#### Use scale_"fill"_manual to change the fill colors  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  scale_x_discrete(name="Region") +
  scale_y_continuous(name="Number of Schools", limits=c(0,500)) +
  scale_fill_manual(values=c("yellow","black"))
```






## Modifying Legends  
#### Load the dataset  
```{r}
college <- read_csv('http://672258.youcanlearnit.net/college.csv')
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree),
         control=as.factor(control), gender=as.factor(gender),
         loan_default_rate=as.numeric(loan_default_rate))
```

#### Create the bar graph  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  scale_x_discrete(name="Region") +
  scale_y_continuous(name="Number of Schools", limits=c(0,500)) +
  scale_fill_manual(values=c("yellow","black"))
```

#### Use scale_"fill"_manual to change the legend title  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  scale_x_discrete(name="Region") +
  scale_y_continuous(name="Number of Schools", limits=c(0,500)) +
  scale_fill_manual(values=c("yellow","black"), guide_legend(title="Institution Type"))
```

#### Use scale_"fill"_manual to adjust the legend formatting  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  scale_x_discrete(name="Region") +
  scale_y_continuous(name="Number of Schools", limits=c(0,500)) +
  scale_fill_manual(values=c("yellow","black"), 
                    guide=guide_legend(title="Institution Type", label.position="bottom", nrow=1, keywidth=2.5))
```

#### Use "theme" to move the legend to the bottom of the plot  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  scale_x_discrete(name="Region") +
  scale_y_continuous(name="Number of Schools", limits=c(0,500)) +
  scale_fill_manual(values=c("yellow","black"), 
                    guide=guide_legend(title="Institution Type", label.position="bottom", nrow=1, keywidth=2.5)) +
  theme(legend.position="bottom")
```

#### Use "theme" to move the legend to the top of the plot  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  scale_x_discrete(name="Region") +
  scale_y_continuous(name="Number of Schools", limits=c(0,500)) +
  scale_fill_manual(values=c("yellow","black"), 
                    guide=guide_legend(title="Institution Type", label.position="bottom", nrow=1, keywidth=2.5)) +
  theme(legend.position="top")
```






## Annotating Plots  
#### Load the dataset  
```{r}
college <- read_csv('http://672258.youcanlearnit.net/college.csv')
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree),
         control=as.factor(control), gender=as.factor(gender),
         loan_default_rate=as.numeric(loan_default_rate))
```

#### Create the scatterplot  
```{r}
ggplot(data=college) +
  geom_point(mapping=aes(x=tuition, y=sat_avg, color=control, size=undergrads), alpha=0.5) 
```

#### Use annotate() to add a text annotation  
```{r}
ggplot(data=college) +
  geom_point(mapping=aes(x=tuition, y=sat_avg, color=control, size=undergrads), alpha=0.5) +
  annotate("text", label="Elite Privates", x=45000,y=1500)
```

#### Use geom_hline() to add a line for the mean SAT score  
```{r}
ggplot(data=college) +
  geom_point(mapping=aes(x=tuition, y=sat_avg, color=control, size=undergrads), alpha=0.5) +
  annotate("text", label="Elite Privates", x=45000,y=1500) +
  geom_hline(yintercept=mean(college$sat_avg))

```

#### Use geom_hline() to label the line  
```{r}
ggplot(data=college) +
  geom_point(mapping=aes(x=tuition, y=sat_avg, color=control, size=undergrads), alpha=0.5) +
  annotate("text", label="Elite Privates", x=45000,y=1500) +
  geom_hline(yintercept=mean(college$sat_avg)) +
  annotate("text", label="Mean SAT", x=47500, y=mean(college$sat_avg)-15)
```

#### Use geom_Vline() to add a line for mean tuition and add a text annotation  
```{r}
ggplot(data=college) +
  geom_point(mapping=aes(x=tuition, y=sat_avg, color=control, size=undergrads), alpha=0.5) +
  annotate("text", label="Elite Privates", x=45000,y=1500) +
  geom_hline(yintercept=mean(college$sat_avg)) +
  annotate("text", label="Mean SAT", x=47500, y=mean(college$sat_avg)-15) +
  geom_vline(xintercept=mean(college$tuition)) +
  annotate("text", label="Mean Tuition", x=mean(college$tuition)+7500, y=700)
```

#### Use scale_to change names  
```{r}
ggplot(data=college) +
  geom_point(mapping=aes(x=tuition, y=sat_avg, color=control, size=undergrads), alpha=0.5) +
  annotate("text", label="Elite Privates", x=45000,y=1500) +
  geom_hline(yintercept=mean(college$sat_avg), color="dark grey") +
  annotate("text", label="Mean SAT", x=47500, y=mean(college$sat_avg)-15) +
  geom_vline(xintercept=mean(college$tuition), color="dark grey") +
  annotate("text", label="Mean Tuition", x=mean(college$tuition)+7500, y=700) +
  theme(panel.background = element_blank(), legend.key = element_blank()) +
  scale_color_discrete(name="Institution Type") +
  scale_size_continuous(name="Undergraduates") +
  scale_x_continuous(name="Tuition") +
  scale_y_continuous(name="SAT Scores")
```






## Titles  
#### Load the dataset  
```{r}
library(tidyverse)
college <- read_csv('http://672258.youcanlearnit.net/college.csv')
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree),
         control=as.factor(control), gender=as.factor(gender),
         loan_default_rate=as.numeric(loan_default_rate))
```

#### Create the bar graph  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  scale_x_discrete(name="Region") +
  scale_y_continuous(name="Number of Schools", limits=c(0,500)) +
  scale_fill_manual(values=c("yellow","black"), 
                    guide=guide_legend(title="Institution Type", label.position="bottom", nrow=1, keywidth=2.5)) +
  theme(legend.position="bottom")
```

#### Add a title  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  scale_x_discrete(name="Region") +
  scale_y_continuous(name="Number of Schools", limits=c(0,500)) +
  scale_fill_manual(values=c("yellow","black"), 
                    guide=guide_legend(title="Institution Type", label.position="bottom", nrow=1, keywidth=2.5)) +
  theme(legend.position="bottom") +
  ggtitle("More colleges are in the southern U.S. than any other region.")
```

#### Add a subtitle  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme(panel.background=element_blank()) +
  theme(plot.background=element_blank()) +
  scale_x_discrete(name="Region") +
  scale_y_continuous(name="Number of Schools", limits=c(0,500)) +
  scale_fill_manual(values=c("yellow","black"), 
                    guide=guide_legend(title="Institution Type", label.position="bottom", nrow=1, keywidth=2.5)) +
  theme(legend.position="bottom") +
  ggtitle("More colleges are in the southern U.S. than any other region.", 
          subtitle="Source: U.S. Department of Education")
```






## Themes  
#### Load the dataset  
```{r}
college <- read_csv('http://672258.youcanlearnit.net/college.csv')
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree),
         control=as.factor(control), gender=as.factor(gender),
         loan_default_rate=as.numeric(loan_default_rate))
```

#### Create the bar graph  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control))
```

#### Black and white theme  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme_bw()
```

#### Minimal theme  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme_minimal()
```

#### Void theme  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme_void()
```

#### Dark theme  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme_dark()
```

#### ggthemes Package  
```{r}
library(ggthemes)
```

#### Solarized theme  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme_solarized()
```

#### Excel theme  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme_excel()
```

#### Wsj theme  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme_wsj()
```

#### Econimist theme  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme_economist()
```

#### Fivethirtyeight theme  
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control)) +
  theme_fivethirtyeight()
```