---
title: "ggplot2_Geometry Type"
author: "Bing-Je_Wu"
date: "8/17/2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

## Outlines
  * Scatterplots  
  * Lines and Smoothers  
  * Bars and Columns   
  * Histograms  
  * Boxplots  


## Scatterplots 
#### Load the datase
```{r}
library(tidyverse)
college <- read_csv('http://672258.youcanlearnit.net/college.csv')
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree),
         control=as.factor(control), gender=as.factor(gender),
         loan_default_rate=as.numeric(loan_default_rate))

colSums(is.na(college))
```

#### Simple scatterplot
```{r}
ggplot(data=college) +
  geom_point(mapping=aes(x=tuition, y=sat_avg))
```

#### We can do this using the shape attribute
```{r}
ggplot(data=college) +
  geom_point(mapping=aes(x=tuition, y=sat_avg, shape=control))
```

#### We can use color
```{r}
ggplot(data=college) +
  geom_point(mapping=aes(x=tuition, y=sat_avg, color=control))
```

#### We can use color to represent the number of students
```{r}
ggplot(data=college) +
  geom_point(mapping=aes(x=tuition, y=sat_avg, color=control, size=undergrads))
```

#### And, lastly, we ca add some transparency so we can see through those points a bit
```{r}
ggplot(data=college) +
  geom_point(mapping=aes(x=tuition, y=sat_avg, color=control, size=undergrads), alpha=0.5)
```



## Lines and Smoothers
#### Load the dataset 
```{r}
library(tidyverse)
college <- read_csv('http://672258.youcanlearnit.net/college.csv')
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree),
         control=as.factor(control), gender=as.factor(gender),
         loan_default_rate=as.numeric(loan_default_rate))
```

#### We use line graph instead of scatterplots
```{r}
ggplot(data=college) +
  geom_line(mapping=aes(x=tuition, y=sat_avg, color=control))
```

#### Add oints back in
```{r}
ggplot(data=college) +
  geom_line(mapping=aes(x=tuition, y=sat_avg, color=control)) +
  geom_point(mapping=aes(x=tuition, y=sat_avg, color=control))
```

#### Alternative code
```{r}
ggplot(data=college, mapping=aes(x=tuition, y=sat_avg, color=control)) +
  geom_line() +
  geom_point()
```

#### Add geom_smooth geometry to fit a line instead of connecting every point
```{r}
ggplot(data=college, mapping=aes(x=tuition, y=sat_avg, color=control)) +
  geom_smooth() +
  geom_point()
```

#### Add transparency to just the points to make the line stand out more
```{r}
ggplot(data=college, mapping=aes(x=tuition, y=sat_avg, color=control)) +
  geom_smooth() +
  geom_point(alpha=0.5)
```

#### Remove the confidence interval from the smoother
```{r}
ggplot(data=college, mapping=aes(x=tuition, y=sat_avg, color=control)) +
  geom_smooth(se=FALSE) +
  geom_point(alpha=1/5)
```




## Bars and Columns

*bar graph: uses count as the y-axis value*

*col graph: allows user to specify y-axis value*

#### Load the dataset
```{r}
library(tidyverse)
college <- read_csv('http://672258.youcanlearnit.net/college.csv')
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree),
         control=as.factor(control), gender=as.factor(gender),
         loan_default_rate=as.numeric(loan_default_rate))
```

#### Use bar graph to get the counts of schools in each region?
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region))
```

#### Break it out by public vs. private
```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control))
```

#### What is average tuition by region?
Use dplyr to create the right tibble first
```{r}
college %>%
  group_by(region) %>%
  summarize(average_tuition=mean(tuition))
```

#### If use geom_bar on y-axis, it must have stat = "identity"
```{r}
college %>%
  group_by(region) %>%
  summarize(average_tuition=mean(tuition)) %>%
  ggplot() +
  geom_bar(mapping=aes(x=region, y=average_tuition), stat="identity")
```

#### Use geom-col instead
```{r}
college %>%
  group_by(region) %>%
  summarize(average_tuition=mean(tuition)) %>%
  ggplot() +
  geom_col(mapping=aes(x=region, y=average_tuition))
```





## Histograms
#### Load the dataset
```{r}
library(tidyverse)
college <- read_csv('http://672258.youcanlearnit.net/college.csv')
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree),
         control=as.factor(control), gender=as.factor(gender),
         loan_default_rate=as.numeric(loan_default_rate))
```

#### Use Histograms to bin

```{r}
ggplot(data=college) +
  geom_histogram(mapping=aes(x=undergrads), boundary=0)  #- boundary = origin point

```

#### Seperate into 4 bins
```{r}
ggplot(data=college) +
  geom_histogram(mapping=aes(x=undergrads), bins=4, boundary=0)
```

#### Seperate into 10 bins
```{r}
ggplot(data=college) +
  geom_histogram(mapping=aes(x=undergrads), bins=10, boundary=0)
```

#### Specify the width of the bins
```{r}
ggplot(data=college) +
  geom_histogram(mapping=aes(x=undergrads), binwidth=1000, boundary=0)
```





## Boxplots
#### Load the dataset as described in Video 1.3
```{r}
library(tidyverse)
college <- read_csv('http://672258.youcanlearnit.net/college.csv')
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree),
         control=as.factor(control), gender=as.factor(gender),
         loan_default_rate=as.numeric(loan_default_rate))
```

#### Use scatter plot to see tuition vs. institutional control
```{r}
ggplot(data=college) +
  geom_point(mapping=aes(x=control, y=tuition))
```

#### Use jitter instead
```{r}
ggplot(data=college) +
  geom_jitter(mapping=aes(x=control, y=tuition))
```

#### Boxplot
```{r}
ggplot(data=college) +
  geom_boxplot(mapping=aes(x=control, y=tuition))
```
